An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/trans.tex
better trans

The translator takes as input a sample dataset of configuration files and transforms it into another set of files written in
typed and well-structured representations.
The translator can be seen a parser, and it is only
used to generate an intermediate representation for the post
process, such as learning rules (see $\S$\ref{sec-learn}).
Coupled with rules generated by learner module,
we will have a complete language model to verify configuration files
of our interest.

Translating or parsing is system dependent. In other words, for MySQL
and HDFS, we need to develop different parsers to handle each of them,
respectively. \app allows users to 
provide an extra help to the translator
for their specific system configurations,
but it is not required.

The majority of entries in a configuration files are assignments.Our first attempt was to simply
translate every key-value entry {\tt {k = v}} into a triple $(k, v, \tau)$, where $\tau$ is a type of 
$v$. However, sometimes we could not fully determine the type of key 
based on a single example value. For this reason, we introduced {\emph {probabilistic types}}.

@@

In \app set $\mathcal{T}$ contains strings, integers, file paths, 
sizes and IP addresses. With every type we associate a list of templates 
that are use to learn the rules about that files. Table~\ref{table:kysymys} contains
the most important types and templates.

\begin{table}
  \begin{tabular}{| l |  l |}
    \hline
    Type & Operation  \\ \hline
    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
    String & $U = V, U \neq V, \textsf{prefix}(U,V), \textsf{sufix}(U,V), \ldots$   \\ \hline
    File & $\textsf{file}(F), \textsf{dir}(D),\ldots$   \\ \hline
    Size & similar as for integers   \\ \hline
    Port &    \\ \hline
    IP Addr.  &   \\

@@

\para{Formal Intermediate Representation.}

An additional problem is that configuration files sometimes contain a simple version of the {\tt {if-then}} which 
sets under which conditions some actions should be applied.

The formal grammar we use for our intermediate representation presented in the following. 
Firstly, we make a list of the possible types for a configuration file. This is present in 
Secondly, we

We come up with the following types:

1. Port 
The $i$-th entry inside an intermediate representation corresponding to a 
translated file

We declare a quadruple $(g,k,v,\{\tau_1, \ldots, \tau_n\}_i$
We need a kind of formal definition (using a figure) to
define the grammar of our intermediate representation. The basic
view of this definition should be similar to define a type language
grammar.

>>>>

The translator takes as input a sample dataset of configuration files and transforms it into another set of files written in
typed and well-structured representations.
The translator can be seen a parser, and it is only
used to generate an intermediate representation for post-processing, 
such as learning rules (see $\S$\ref{sec-learn}).
Coupled with rules generated by learner module,
we will have a complete language model to verify configuration files
of our interest.

Translating or parsing is system dependent. In other words, for MySQL
and HDFS, we need to develop different parsers to handle each of them,
respectively. \app allows users to 
provide extra help to the translator
for their specific system configurations,
but it is not required.

The majority of entries in a configuration files are assignments. Our first attempt was to simply
translate every key-value entry {\tt {k = v}} into a triple $(k, v, \tau)$, where $\tau$ is a type of 
$v$. However, sometimes we could not fully determine the type of key 
based on a single example value. For this reason, we introduced {\emph {probabilistic types}}.

@@

In \app, the set $\mathcal{T}$ contains strings, integers, file paths, 
sizes, and IP addresses. With every type, we associate a list of templates 
that are used to learn the rules about those files. Table~\ref{table:kysymys} contains
the most important types and templates.

\begin{table}
  \begin{tabular}{| l |  l |}
    \hline
    Type & Operation  \\ \hline
    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
    String & $\textsf{substr}(U, V), \textsf{prefix}(U,V), \textsf{suffix}(U,V), \ldots$   \\ \hline
    File Path & $\textsf{isFile}(F), \textsf{isDir}(D),\ldots$   \\ \hline
    Size & Similar to integers   \\ \hline
    Port & $P_1 > P_2$ \\ \hline
    IP Addr.  & $\textsf{sameSubnet}(addr1, addr2)$   \\

@@

In general, the templates works as follows: if there are two entries ${\tt {k1 = v1}}$ and 
${\tt {k2 = v2}}$, let $t(X, Y)$ be a template that can be applied to those values (w.r.t. their types).
If $t(v1, v2)$ holds, \ie the template condition is valid for those concrete values, then we will add a rule
$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a relation between variables.

With the help of probabilistic types, we addressed ambiguities during the parsing phase. Another problem that we need to solve
is that configuration files sometimes contain a simple version of the {\tt {if-then}}, such as in Apache HTTPD, that 
sets conditions under which some action should be applied. Therefore, we also add this guard to our entry 
during the parsing phase. We first check if the guard is true before deriving a rule; otherwise, we skip the entry.

To summarize, the translator translates every entry ${\tt {k = v}}$ in a configuration file into a quadruple 
$$(g,k,v,\textsf{List}[p_1:\tau_1, \ldots, p_n:\tau_n])$$

For an entry, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the  
type list by $typelist(e)$.
